$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-05 paper/e6ssm-tuning-paper.tex
Added two-loop beta for m_{H_u}^2, fixed some typos in two-loop beta for m_{Q3}^2

\beta_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2BetaTwoLoop}\\

@@

&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+g_2^4\left [ 87M_2^2+m_{\overline{H'}}^2+m_{H'}^2+3\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\

@@

&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\

>>>>

\beta_{m_{H_u}^2}^{(2)}&=-36y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )-6y_t^2y_b^2\left ( m_{H_u}^2+m_{H_d}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
&{}-72y_t^2a_t^2-6\left ( y_ta_b+y_ba_t\right )^2-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_{\lambda}^2\nonumber\\
&{}-\lambda^2\sum_{i=1}^3\bigg [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\nonumber\\
&{}+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\bigg ]-\sum_{i=1}^3 \big [4\left ( \lambda_ia_{\lambda}+\lambda a_{\lambda_i}\right )^2\nonumber\\
&{}+6\left ( \kappa_i a_{\lambda}+\lambda a_{\kappa_i}\right )^2\big ]-6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
&{}-2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )-6\left ( \lambda a_b+y_ba_{\lambda}\right )^2-2\left ( \lambda a_\tau+y_\tau a_{\lambda}\right )^2\nonumber\\
&{}+32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )+32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
&{}+\frac{2}{5}g_1^2y_t^2\left ( -5m_{H_u}^2+m_{Q3}^2+16m_{u3}^2+8M_1^2\right )+\frac{8}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
&{}+\frac{6}{5}g_1^2y_b^2\left ( 3m_{H_d}^2-m_{Q3}^2-2m_{d3}^2\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2-2m_{e3}^2\right )\nonumber\\
&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{Di}^2-m_{\overline{D}i}^2\right )\right ]\nonumber\\
&{}+12g_1'^2y_t^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )\nonumber\\
&{}+12g_1'^2\left ( Q_Q^2+Q_u^2-Q_2^2\right )\left ( a_t^2-2y_ta_tM_1'\right )-24Q_2g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
&{}-24Q_2g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )-8Q_2g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )\nonumber\\
&{}+4g_1'^2\lambda^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
&{}+4g_1'^2\left ( Q_1^2-Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )\nonumber\\
&{}-4Q_2g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )+3\kappa_i^2\left ( Q_Sm_S^2+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2\right )\right ]\nonumber\\
&{}+\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{\overline{D}i}^2-m_{Di}^2\right )\nonumber\\
&{}+32Q_2g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+Q_Dm_{Di}^2\right )\nonumber\\
&{}+3g_2^4\left [ 29M_2^2+m_{H'}^2+m_{\overline{H'}}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\
&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{\overline{H'}}^2-m_{H'}^2+\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
&{}+12Q_2g_2^2g_1'^2\bigg [ 2Q_2\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{\overline{H'}}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 10m_{di}^2+2m_{Di}^2+10m_{\overline{D}i}^2+54m_{ei}^2+18m_{H_i^u}^2+4m_{Qi}^2-8m_{ui}^2\right )\bigg ]\nonumber\\
&{}+\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_2\big ( 3Q_d+Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+4Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}m_{H'}^2\nonumber\\
&{}+3\sum_{i=1}^3\left ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{Li}^2\right.\nonumber\\
&{}\left.+Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\right )+9Q_2Q_{\overline{H'}}m_{\overline{H'}}^2-3Q_2Q_{H'}m_{H'}^2+Q_2\sum_{i=1}^3\left ( 8Q_dm_{di}^2+8Q_{\overline{D}}m_{\overline{D}i}^2\right.\nonumber\\
&{}\left.-4Q_Dm_{Di}^2+12Q_em_{ei}^2-3Q_1m_{H_i^d}^2+9Q_2m_{H_i^u}^2-3Q_Lm_{Li}^2+7Q_Qm_{Qi}^2-4Q_um_{ui}^2\right )\bigg ]\nonumber\\
&{}+8Q_2g_1'^4\bigg [ 3Q_2M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+6Q_1^2+8Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2\nonumber\\
&{}+3Q_D^3m_{Di}^2+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHu2BetaTwoLoop}\\

@@

&{}+Q_Dm_{Di}^2+Q_{\overline{D}}m_{\overline{D}i}^2 \big )\bigg ]+3g_2^4\left [ 29M_2^2+m_{\overline{H'}}^2+m_{H'}^2+\sum_{i=1}^3\left ( 3m_{Qi}^2+m_{Li}^2+m_{H_i^d}^2+m_{H_i^u}^2\right )\right ]\nonumber\\

@@

&{}+10Q_Q-18Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
